### 2020-06-28 response/response-demography-3.tex

\begin{enumerate}

\item We note that you kept to the table/figure limit; however, some of
the figures are several pages long and relatively small. These will have
to be evaluated at the copy edit stage as there is no obvious quick fix
- the figures reflect the analyses carried out (and some additional ones
are in an online appendix). Please make sure to submit as
high-resolution image as possible in the format required by the journal.
We are somewhat concerned about figure/table size within the print form
of the journal.

[Response:]

TK review titles of figures and table to be better reflect the
analyses undertaken.

@@

\section*{Deputy Editor}

\begin{enumerate}

\item The overall topic and research question is not clear in the
introduction. The main topic relates to changes in birth spacing over
time, which are influenced by sex selection/sex composition and maternal
education, and how this affects fertility and infant mortality. This is
a long list of interesting questions and analyses but this is confusing
for the reader. It would be useful to have a succinct statement about
what the study is about (what are key independent variables/concepts and
key outcomes) and place that in the introduction and before the data and
analyses section. This way, the reader can understand why the analyses
will proceed in a particular order and what is being tested. In
addition, the titles of the figures and tables should be reviewed to see
if they could better reflect the analyses undertaken. Overall, the
reader needs to be reminded at the beginning and in each section what
you aim to do.

[Response:] I have rewritten the Introduction to emphasize the main question I address
(``how did birth spacing respond to these changes, especially the introduction and spread 
of sex selection?'') and the two questions addressing the effects of changes in 
birth spacing (``to what extent do changes in birth spacing bias our standard fertility 
estimates?'' and `` how do the changes in birth spacing and the increased use of abortions 
impact children's chances of survival?'').

Following the three questions, I now outline how the study progresses focusing on 
how I examine each of the three questions, including the key outcomes and key explanatory 
variables.
To prevent exceeding the word count I have also edited the entire introduction.
Although sligthly longer than original, it is still less than 900 words 
(not counting references).

I have edited the introduction of each section to highlight what I question
I am addressing.
Furthermore, I have removed some of the repetition in, for example, the
discussion of tempo effects and mortality, so that the motivation is now only
in the Introduction rather than being spread over the Introduction and the
relevant sections.

TK I address the issue of the figure and table title above.

### 2020-06-28 paper/sex_selection_spacing-ver4.tex
Initial combine of spacing sections w/o edits

\section{Distribution of Birth Spacing}

@@

\section{What has Happened to Fertility?\label{sec:fertility}}

@@

Table \ref{tab:fertility} shows the two fertility measures by urban/rural and education.
Because the hazard model predictions only use births up to parity four, I calculate
fertility rates using only the same births.
Hence, my fertility rates are not directly comparable to those in the NFHS reports.
Otherwise, I follow the procedure used in the NFHS reports \citep{Croft2018}.
I calculate age-specific fertility rates for five-year age groups using the number of 
births in months 1 to 36 before the survey month and the number of women in each age 
group.

>>>>

\subsection{Distribution of Birth Spacing}

@@

\subsection{Interpretation}

\section{What Happened to Fertility?\label{sec:fertility}}

@@

Table \ref{tab:fertility} shows the two fertility measures by urban/rural and education.
Because the hazard model predictions only use births up to parity four, I calculate
fertility rates using only the same births.
Hence, my fertility rates are not directly comparable to those in the NFHS reports,
but otherwise, I follow the procedure used in the NFHS reports \citep{Croft2018}.
I calculate age-specific fertility rates for five-year age groups using the number of 
births in months 1 to 36 before the survey month and the number of women in each age 
group.
